---
title: "Accessibility practices for Deaf and Hard-of-Hearing people"
author: "Andrea Sánchez-Tapia"
subtitle: "The Turing Way BookDash Nov 2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
options(servr.daemon = TRUE)#para que no bloquee la sesión
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#035AA6",
  colors = c(
    red = "#A70000",
    purple = "#88398a",
    orange = "#ff8811",
    green = "#136f63",
    blue = "#4B4FFF"
  ),
  header_font_google = google_font("Roboto Condensed"),
  text_font_google = google_font("Roboto Condensed", "300", "300i"),
  code_font_google = google_font("Fira Mono"), text_font_size = "28px"
)
#xaringanExtra::use_logo(image_url = "url('figs/LatinR_LOGOS-21.png')")
```

# References

+ Huyck, J.J., Anbuhl, K.L., Buran, B.N., et al., 2021. Supporting Equity and Inclusion of Deaf and Hard-of-Hearing Individuals in Professional Organizations. Frontiers in Education 6, 417. https://doi.org/10.3389/feduc.2021.755457

+ _Very localized_ experience in Brazil, where LIBRAS (Lingua brasileira de sinais) is the official sign language

---
# Three types of access

+ __Physical access:__ whether an individual can enter, move around, and function, interact with materials in a space. Technical aspects. Microphones, captioning, sign language interpretation. Rooms that are compatible with hearing aids.

--

+ __Social access:__ attending and being able to interact in the _social aspects_ of the community.  
<!--but also being the only one in the room!-->

--

+ __Financial access:__ Health care and assistive technology, hiring and paying for the services too. Individualized solutions put a burden on individuals and this is unbalanced towards low-income families. 

---
## A five pillar model

1. Foster mentoring programs 

2. Proactively giving equal access

3. Easing financial burdens

4. Recruiting for leadership positions

5. Establishing a culture of equity and inclusion


---
## Some considerations 

+ Captioning can work for non-Native English speakers as well, people with technical issues and lifts a cognitive burden on the audience

<!-- CC is absolutely widespread today --> 

+ Sign languages vary from country to country, even with regional and cultural variations, but in some countries they are widely used and prefered over captions

---
class: center, middle, inverse

# Thanks!
